The Community Land Model, version 5.1 \\ One-at-a-time Parameter Perturbation Ensemble

### 2024-08-13 ms/ms.tex
overleaf

Given the large parameter space, to conduct an initial analysis of the response of the model to parametric uncertainty, we decided to vary each parameter independently, exploring the impact of low and high values. To define parameter ranges we created an online spreadsheet and solicited domain-area experts to provide a minimum and maximum value for each parameter. In some cases literature values were directly utilized, but in many cases, expert judgment was used. The spreadsheet, with literature references and parameter descriptions is available online and in appendix zqz. In some cases parameters could not or should not be perturbed independently, because they feature inherent co-dependence. In the case of nitrogen fixation costs, we opted to perturb the parameters independently, but also as a group (`KCN'), to enforce a change in overall nitrogen limitation in lieu of switching from one uptake pathway to another. We likewise opted to perturb soil hydraulic parameters directly (e.g. saturated hydraulic conductivity) and also via perturbations to the soil texture (percent sand, clay, and silt).

@@

\subsection{Experimental Design}
\label{sect:exp}
For each of the 211 parameters, we ran 12 simulations, one for each the minimum and maximum parameter values, across six different forcing scenarios.
Each simulation ran for 150 years, with the first 140 for spin-up (as described above in Section \ref{sect:mcn}), followed by a 10-year period for analysis.
It is important to note that these are equilibrium-style simulations, where the land has been allowed to reach steady state conditions relative to the climate forcing. This is achieved by repeating the same 10-year forcing dataset 14 times during the spin-up procedure. As such these simulations are not directly comparable to transient simulations or satellite observations, where present-day vegetation has not yet reached equilibrium with present-day CO$_2$.

@@

\subsection{Analyses}

Biome analysis (Supp Figures S2-4)

>>>>

Given the large parameter space, to conduct an initial analysis of the response of the model to parametric uncertainty, we decided to vary each parameter independently, exploring the impact of low and high values. To define parameter ranges we created an online spreadsheet and solicited domain-area experts to provide a minimum and maximum value for each parameter. In some cases literature values were directly utilized, but in many cases, expert judgment was used. The spreadsheet, with literature references and parameter descriptions is available online and in appendix zqz. In some cases parameters could not or should not be perturbed independently, because they feature inherent co-dependence. In the case of nitrogen fixation costs, we opted to perturb the parameters independently, but also as a group (`KCN'), to enforce a change in overall nitrogen limitation in lieu of switching from one uptake pathway to another. We likewise opted to perturb soil hydraulic parameters directly (e.g. saturated hydraulic conductivity) and also separately via perturbations to the soil texture (percent sand, clay, and silt).

@@

\subsection{Experimental Design}
\label{sect:exp}
For each of the 211 parameters, we ran 12 simulations, one for each the minimum and maximum parameter values, across six different forcing scenarios.
Each simulation ran for 150 years, with the first 140 for spin-up (as described above in Section \ref{sect:mcn}), followed by a 10-year period for analysis.
It is important to note that these are equilibrium-style simulations, where the land has been allowed to reach steady state conditions relative to the climate forcing. This is achieved by repeating the same 10-year forcing dataset 15 times during the spin-up procedure and production phase of our simulations. As such these simulations are not directly comparable to transient simulations or satellite observations, where present-day vegetation has not yet reached equilibrium with present-day CO$_2$.

@@

\subsection{Biome definitions}
In addition to analyzing parameter effects on various output variables globally, we were also interested in understanding parameter effects on different biomes.
As such, we categorized each of the 400 sparse grid cells according to their Whittaker biome, which delineates biomes based on average temperature and precipitation \cite{whittaker1970}. 
Biomes were delineated based on the atmospheric forcing temperature and precipitation data averaged across 2005 to 2014 (Supp Figure S6).
Overall there are nine vegetated biomes and an additional ice sheet biome, where no vegetation is present (Supp Figures S7,8).
